---
title: "My fantastic analysis"
format: 
  html:
    self-contained: true
date: now
author: "Squidward P. Tentacles"
---

In this analysis I'm going to use the `mtcars` dataset to
demonstrate regression and prediction.

## Libraries

Here are the necessary libraries you'll need to replicate this...

```{r}
library(ggplot2)
```

## Fitting the model

I chose to use the `wt` an `hp` variables as predictors because blah blah blah...

```{r}
model <- lm(mpg ~ wt + hp, data = mtcars)
```

## Predict on New Data

I'm creating some new data to predict on...

```{r}
new_data <- data.frame(wt = c(2.5, 3.0, 3.5), hp = c(100, 150, 200))
predictions <- predict(model, newdata = new_data)
```

And plotting it with ggplot:
```{r}
plot <- ggplot(new_data, aes(x = wt, y = hp)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  geom_text(aes(label = round(predictions, 2)), vjust = -1, color = "red") +
  labs(title = "Predicted MPG based on Weight and Horsepower",
       x = "Weight (1000 lbs)",
       y = "Horsepower")
plot
```

## Conclusion

In this notebook I ran an experiment and documented it so that next time
I or someone else sees it they can know exactly what I did
and why ðŸ˜
